From Reversible Programs to \\ Univalent Universes and Back

### 2021-09-05 Pi+/paper/finite.tex

\begin{proposition}[Universal property of $F(\langle A ; R \rangle)$]
  Given a group $G$ and a map $f : A \to G$, such that $f$ extended to $F(A)$ respects $R$, there is a unique group
  homomorphism $\extend{f} : F(\langle A ; R \rangle) \to^G G$ such that $\extend{f} \comp \eta_A \htpy f$.
\end{proposition}

>>>>

\begin{proposition}[Universal property of $F(\langle A ; R \rangle)$]
  Given a group $G$ and a map $f : A \to G$, such that $f$ extended to $F(A)$ respects $R$, there is a unique group
  homomorphism $\extend{f} : \term{Hom}(F(\langle A ; R \rangle), G)$ such that $\extend{f} \comp \eta_A \htpy f$.
\end{proposition}
